Verifying Demonstrations

### 2017-07-28 properties.tex
Changes relation from < to \prec

    \item A\ref{SpatiallyRelated} can be provided by \iacf{LP}.
  \end{itemize}
\end{idea}
}
\end{frame}
\Cref{CreatedBeforeEnd,CreatedAfterStart} requires a \emph{strict partial 
  order}\footnote{%
  A relation \(<\) which is irreflexive, antisymmetric and transitive.
}.
If some objects in the set relate to known points in time, then the partial 
order allows to relate the data to the time of the event.
\Cref{SpatiallyRelated} binds the data spatially to the event.

>>>>

    \item A\ref{SpatiallyRelated} can be provided by \iacf{LP}.
  \end{itemize}
\end{idea}
}
\end{frame}
\Cref{CreatedBeforeEnd,CreatedAfterStart} requires a \emph{strict partial 
  order}\footnote{%
  A relation \(\prec\) which is irreflexive, antisymmetric and transitive.
}.
If some objects in the set relate to known points in time, then the partial 
order allows to relate the data to the time of the event.
\Cref{SpatiallyRelated} binds the data spatially to the event.
